Extrinsic Type Inference (DRAFT 2025-06-08)

### 2025-07-09 extrinsic_type_inference_paper/paper.tex
update notes and notation

    \inferrule {
      \Theta, \Delta, \Gamma \entails e \hastype \tau \given  \Theta', \Delta'
      \\
      \Theta', \Delta' \entails \tau \subtypes \alpha_\nu \rightarrow \Pi_\nu
      \\\\
      \alpha_\nu \downarrow \Pi_\nu
      \fallingdotseq 
      \alpha_\mu \uparrow \Pi_\mu
      \\
      \textbf{pack}^-(\textbf{ftv}(\Delta')\ \alpha_\mu \entails \Pi_\mu) = \tau_\mu
      \\\\
      \factorsinto \J{LFP[} \alpha_\mu \J{]}\tau_\mu \subtypes \J{left} \mapsto \tau_l
      \\
      \factorsinto \J{LFP[} \alpha_\mu \J{]}\tau_\mu \subtypes \J{right} \mapsto \tau_r
    } {
      \Theta, \Delta, \Gamma \entails \J{loop(}e\J{)} 
      \hastype 
      \tau_l \J{->} \tau_r
      \given \Theta', \Delta'
    }
  \end{mathpar}
\end{definition}

@@

\TODO{discuss recursive types}

\TODO{discuss regular trees}

\TODO{look into the issue of caching related to recursion}

>>>>

    \inferrule {
      \Theta, \Delta, \Gamma \entails e \hastype \tau \given  \Theta', \Delta'
      \\
      \Theta', \Delta' \entails \tau \subtypes \alpha \rightarrow \Pi
      \\\\
      \alpha \downarrow \Pi
      \fallingdotseq 
      \alpha' \uparrow \Pi'
      \\
      \textbf{pack}^-(\textbf{ftv}(\Delta')\ \alpha' \entails \Pi') = \tau'
      \\\\
      \factorsinto \J{LFP[} \alpha' \J{]}\tau' \subtypes \J{left} \mapsto \tau_l
      \\
      \factorsinto \J{LFP[} \alpha' \J{]}\tau' \subtypes \J{right} \mapsto \tau_r
    } {
      \Theta, \Delta, \Gamma \entails \J{loop(}e\J{)} 
      \hastype 
      \tau_l \J{->} \tau_r
      \given \Theta', \Delta'
    }
  \end{mathpar}
\end{definition}

@@

\TODO{discuss implicit and flow based approaches}

\TODO{enumerate the various work with various type forms}

\TODO{note how our structural requirements on recursive types prevent typing generators}

\TODO{note the distinction between our least fixed point types and the more general 
recursive types}
